A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-20 paper.tex
Intro brainstorm

@@

@@

If $\fg$ carries a nondegenerate invariant symmetric paiirng of degree $d$, so does $\fg_{\Hod}$.

@@

\begin{theorem}
\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation maybe doesn't come from dimensional reduction?} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
\end{theorem}

>>>>

\chris{Possible topics for the introduction
\begin{enumerate}
 \item  Context and literature on twists, including in the BV formalism.  There's a perspective there in terms of derived algebraic geometry (our mapping stacks we like to talk about).  Also at least a remark on the perspective in terms of coupling to twisted sugra.
 \item  perspective in terms of twisting homomorphisms, and putting twisted theories on curved backgrounds.
 \item  Mathematical literature on SUSY Yang-Mills, including Baez-Huerta and references therein.
 \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
 \item  Table of the twists, and commentary on where each has appeared before in the literature.
 \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
 \item  Connection between twisted BV theories and twisted factorization algebras, and therefore to our earlier paper on $\bb E_n$ algebras.
 \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
 \item  Summary of the sections of the paper.
\end{enumerate}}

@@

\subsection*{Acknowledgements}

@@

If $\fg$ carries a nondegenerate invariant symmetric pairing of degree $d$, so does $\fg_{\Hod}$.

@@

\begin{theorem}
\chris{Rank $(1,1)$ deforming to rank $(2,1)$, the former is done above, the deformation doesn't come from dimensional reduction.  However, we know how $(1,0)$ deforms to $(2,0)$ (further supercharge acts by the differential operator $\dd_2$), so apply the same deformation to $(1,1)$.} $\mr{Map}(\CC_{\mr{Dol}} \times \RR^2_{\mr{dR}}, B\gg_{\mr{Hod}})$.
\end{theorem}
